TBD

### 2019-09-13 manuscript/manuscript.Rmd
incorporated minor edits from Jordi

The adaptive landscape provides a powerful framework for understanding how natural selection has shaped the evolution of biodiversity ---from genes to phenotypes to species [@Wright1931; @Simpson1944; @Arnold2001]. More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory], giving insight to the direct and indirect effects of selective constraints [@Arnold1992]. Ecological interactions often play a key role in shaping selective constraints, as evidenced by the role of antagonistic [@Schluter2000; @Abrams2000] and mutualistic [@Bronstein2006] interactions in driving evolutionary change. Although there is clear evidence that species interactions can shape the adaptive landscape, we still have a poor understanding of how the adaptive landscape is shaped by a community of interacting species [@McPeek2017; @terHorst2018]. Resolution on how change in ecological communities shape phenotypic evolution is urgently needed though, given the rapid losses of biodiversity we are observing in the Anthropocene [@Scheffers2016].

@@

```{r Conceptual, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:Conceptual}Experimental manipulation of food-web structure associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*. Black arrows denote the flow of energy in this network of trophic interactions. In the original food web, we allowed the full suite of egg and larval parasitoids to impose selection. In the removal food web, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection. Note that larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid. Larval parasitoids include the following species (from left to right): *Mesopolobus* sp. (Family: Pteromalidae); *Tetrastichus* sp. (Family: Eulophidae); and *Torymus* sp. (Family: Torymidae)."}
knitr::include_graphics("../analyses/complex_simple_foodwebs_v3.jpeg")
```

@@

**Genetic constraints**: The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}$) is governed by the curvature of the adaptive landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:

@@

\begin{table}[H]
\caption{Standardized selection gradients acting on gall midges in the original food web and with the removal of larval parasitoids.}
\label{Table:Gradients}
\centering
\begin{tabular}{lccc}
\\ 
\hline
\textbf{Selection gradient} & \textbf{Original} & \textbf{Removal} & \textbf{Contrast} \\
\hline
$\beta_{\text{Diam}}$ & 
\textbf{
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } & 
\textbf{
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.high,2)`] } & 
\textbf{
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\

@@

```{r UV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the original food web and with the removal of larval parasitoids. Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C). Bold lines represent selection experienced in the original (orange) and removal (blue) food webs (orange). Thin lines represent bootstrapped replicates to show the uncertainty in selection. For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates. Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
knitr::include_graphics("../analyses/UV_landscapes.pdf")
```

@@

```{r MV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in the original food web and with the removal of larval parasitoids. Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C). Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype in each food-web treatment. Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the removal of larval parasitoids compared to the original food web. This indicates that the loss of consumers more strongly favored a specific combination of traits. Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
knitr::include_graphics("../analyses/MV_landscapes.pdf")
```

@@

$$\textbf{C}_{\text{Extinction}} = \begin{pmatrix} 
`r round(extinction_curvs_df["C.Diam","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam","low"],2)`,`r round(extinction_curvs_df["C.Diam","high"],2)`] &  &  \\  
`r round(extinction_curvs_df["C.Diam:Clutch","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam:Clutch","low"],2)`,`r round(extinction_curvs_df["C.Diam:Clutch","high"],2)`] & `r round(extinction_curvs_df["C.Clutch","mean"],2)`\: [`r round(extinction_curvs_df["C.Clutch","low"],2)`,`r round(extinction_curvs_df["C.Clutch","high"],2)`] &  \\  
`r round(extinction_curvs_df["C.Diam:Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam:Pref","low"],2)`,`r round(extinction_curvs_df["C.Diam:Pref","high"],2)`] & `r round(extinction_curvs_df["C.Clutch:Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Clutch:Pref","low"],2)`,`r round(extinction_curvs_df["C.Clutch:Pref","high"],2)`] & `r round(extinction_curvs_df["C.Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Pref","low"],2)`,`r round(extinction_curvs_df["C.Pref","high"],2)`] \end{pmatrix}$$

$$\textbf{C}_{\text{Extinction-Original}} = \begin{pmatrix} 
`r round(difference_curvs_df["C.Diam","mean"],2)`\: [`r round(difference_curvs_df["C.Diam","low"],2)`,`r round(difference_curvs_df["C.Diam","high"],2)`] &  &  \\  
`r round(difference_curvs_df["C.Diam:Clutch","mean"],2)`\: [`r round(difference_curvs_df["C.Diam:Clutch","low"],2)`,`r round(difference_curvs_df["C.Diam:Clutch","high"],2)`] & `r round(difference_curvs_df["C.Clutch","mean"],2)`\: [`r round(difference_curvs_df["C.Clutch","low"],2)`,`r round(difference_curvs_df["C.Clutch","high"],2)`] &  \\  
`r round(difference_curvs_df["C.Diam:Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Diam:Pref","low"],2)`,`r round(difference_curvs_df["C.Diam:Pref","high"],2)`] & `r round(difference_curvs_df["C.Clutch:Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Clutch:Pref","low"],2)`,`r round(difference_curvs_df["C.Clutch:Pref","high"],2)`] & \textbf{`r round(difference_curvs_df["C.Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Pref","low"],2)`,`r round(difference_curvs_df["C.Pref","high"],2)`]} \end{pmatrix}$$

@@

```{r Evolvability, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:Evolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for each food-web treatment. We found that the curvature of the removal food web decreased evolvability in 71% of the G-matrices, suggesting that the loss of consumers tended to decrease evolutionary potential of traits in our study."}
knitr::include_graphics("../analyses/delta_evolvability.pdf")
```

@@

\begin{table}[H]
\caption{Standardized selection gradients acting on egg parasitoids (\textit{Platygaster} sp.)}
\label{Table:ExtendedGradients}
\centering
\begin{tabular}{lc}
\\ 
\hline
\textbf{Selection gradient} & \textbf{Contrast = Original - Extinction}  \\ 
\hline
$\beta_{\text{Diam}}$ &

@@

```{r EggPtoid_Selection, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on egg parasitoids (*Platygaster* sp.). The bold line represents the average difference in the probability of observing the egg parasitoid (original - removal of larval parastioids) as a function of gall midge oviposition preference. Thin lines represent bootstrapped replicates to show the uncertainty in selection. For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates. The decrease in the probability of observing egg parasitoids at high gall-midge densities indicate that larval parasitoids impose nonlinear selection on egg parasitoids."}
knitr::include_graphics("../analyses/selection_on_Platygaster.pdf")
```

@@

<!-- Generality of results -->
The generality of our results likely depends on the relative abundance and functional differences between consumers in a community. For example, if consumers do not differ from each other, then we do not expect the loss of consumers to modify evolutionary constraints. Also, many consumers may be at too low of abundances to impose selection on their resources. Rank abundance curves [@Preston1948] and the disproportionate number of weak interactions in diverse communities [@Paine1992] support this notion. This logic suggests that we may not have observed the effects we did if we had only removed one larval parasitoid, because each species had relatively low abundance [@Barbour2016] and they likely share similar ecological roles. When consumers are functionally different and abundant though, the effect of consumer loss will depend on whether different species impose conflicting selection pressures or select for distinct traits. For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997]. Recent studies in this system have shown that decreases in the relative abundance of birds, due to either small patch sizes [@Start2016] or proximity to urban areas [@Start2018] causes a shift from neutral to directional selection on gall size. On the other hand, different consumers may impose selection on different traits, favoring a particular combination of traits and thus greater selective constraints. Examples of this include strong genetic covariances in plant resistance to different insect herbivores [@Maddox1990; @Wise2007; @Wise2013], although there are also examples where these covariances are weak [@Roche1997; @Barbour2015], or vary from year-to-year [@Johnson2007]. We suggest that gaining predictive insight to the evolutionary consequences of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions. <!--We suggest that gaining predictive insight to the effects of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions.-->

@@

<!--Indirect evolutionary effects-->
Our results suggest that the loss of consumers may not only directly affect connected species, but also result in indirect evolutionary effects. In our study, this indirect effect arises from egg parasitoids being released from intraguild predation when we excluded larval parasitoids. This release occurs more on trees with high larval densities, which could intensify selection on gall midge oviposition preference. A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Pilson1996; @Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @Start2019]. If indirect evolutionary effects are common [@Miller1996; @Walsh2013], then predicting evolutionary trajectories resulting from the loss of consumers will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.

@@

\begin{table}[H]
\caption{Standardized selection gradients imposed by larval parasitoids on gall midges in the original food web. This gives insight to selection acting on gall midges in the absence of the dominant egg parasitoid.}
\label{Table:LarvalGradients}
\centering
\begin{tabular}{lc}
\\ 
\hline
\textbf{Selection gradient} & \textbf{Larval Parasitoids} \\ % & \textbf{Original} 
\hline
$\beta_{\text{Diam}}$ & 
%\textbf{
%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,2)` [
%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } & 
\textbf{
`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam")$mean,2)` [
`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } \\

@@

```{r LarvalPtoid Evolvability, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:LarvalPtoidEvolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for selection in the absence of egg parasitoids vs. the original food web. We found that the curvature imposed by the loss of egg parasitoids decreased evolvability in 57% of the G-matrices, which is smaller in magnitude, but in the same direction, as the effects of losing larval parasitoids."}
knitr::include_graphics("../analyses/larvalptoid_delta_evolvability.pdf")
```

>>>>

The adaptive landscape provides a powerful framework for understanding how natural selection has shaped the evolution of biodiversity ---from genes to phenotypes to species [@Wright1931; @Simpson1944; @Arnold2001]. More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory], giving insight to the direct and indirect effects of selective constraints [@Arnold1992]. Ecological interactions often play a key role in shaping selective constraints, as evidenced by the role of antagonistic and mutualistic interactions in driving evolutionary change [@Schluter2000; @Abrams2000; @Bronstein2006]. Although there is clear evidence that species interactions can shape the adaptive landscape, we still have a poor understanding of how the adaptive landscape is shaped by a community of interacting species [@McPeek2017; @terHorst2018]. Resolution on how change in ecological communities shape phenotypic evolution is urgently needed though, given the rapid losses of biodiversity we are observing in the Anthropocene [@Scheffers2016].

@@

```{r Conceptual, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:Conceptual}Experimental manipulation of food-web structure associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*. Black arrows denote the flow of energy in this network of trophic interactions. In the original food web, we allowed the full suite of egg and larval parasitoids to impose selection. In the removal food web, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection. Note that larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid. Larval parasitoids include the following species (from left to right): *Mesopolobus* sp. (Family: Pteromalidae); *Tetrastichus* sp. (Family: Eulophidae); and *Torymus* sp. (Family: Torymidae)."}
knitr::include_graphics("../analyses/complex_simple_foodwebs_v3.jpeg")
```

@@

**Genetic constraints**: The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}$) are governed by the curvature of the adaptive landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:

@@

\begin{table}[h]
\caption{Standardized selection gradients acting on gall midges in the original food web and with the removal of larval parasitoids.}
\label{Table:Gradients}
\centering
\begin{tabular}{lccc}
\\ 
\hline
\textbf{Selection gradient} & \textbf{Original} & \textbf{Removal} & \textbf{Contrast} \\
\hline
$\beta_{\text{Diam}}$ & 
\textbf{
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } & 
\textbf{
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean,2)` [
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.high,2)`] } & 
\textbf{
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\

@@

```{r UV_Landscape, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the original food web and with the removal of larval parasitoids. Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C). Bold lines represent selection experienced in the original (orange) and removal (blue) food webs (orange). Thin lines represent bootstrapped replicates to show the uncertainty in selection. For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates. Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
knitr::include_graphics("../analyses/UV_landscapes.pdf")
```

@@

```{r MV_Landscape, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in the original food web and with the removal of larval parasitoids. Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C). Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype in each food-web treatment. Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the removal of larval parasitoids compared to the original food web. This indicates that the loss of consumers more strongly favored a specific combination of traits. Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
knitr::include_graphics("../analyses/MV_landscapes.pdf")
```

@@

$$\textbf{C}_{\text{Removal}} = \begin{pmatrix} 
`r round(extinction_curvs_df["C.Diam","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam","low"],2)`,`r round(extinction_curvs_df["C.Diam","high"],2)`] &  &  \\  
`r round(extinction_curvs_df["C.Diam:Clutch","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam:Clutch","low"],2)`,`r round(extinction_curvs_df["C.Diam:Clutch","high"],2)`] & `r round(extinction_curvs_df["C.Clutch","mean"],2)`\: [`r round(extinction_curvs_df["C.Clutch","low"],2)`,`r round(extinction_curvs_df["C.Clutch","high"],2)`] &  \\  
`r round(extinction_curvs_df["C.Diam:Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam:Pref","low"],2)`,`r round(extinction_curvs_df["C.Diam:Pref","high"],2)`] & `r round(extinction_curvs_df["C.Clutch:Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Clutch:Pref","low"],2)`,`r round(extinction_curvs_df["C.Clutch:Pref","high"],2)`] & `r round(extinction_curvs_df["C.Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Pref","low"],2)`,`r round(extinction_curvs_df["C.Pref","high"],2)`] \end{pmatrix}$$

$$\textbf{C}_{\text{Removal-Original}} = \begin{pmatrix} 
`r round(difference_curvs_df["C.Diam","mean"],2)`\: [`r round(difference_curvs_df["C.Diam","low"],2)`,`r round(difference_curvs_df["C.Diam","high"],2)`] &  &  \\  
`r round(difference_curvs_df["C.Diam:Clutch","mean"],2)`\: [`r round(difference_curvs_df["C.Diam:Clutch","low"],2)`,`r round(difference_curvs_df["C.Diam:Clutch","high"],2)`] & `r round(difference_curvs_df["C.Clutch","mean"],2)`\: [`r round(difference_curvs_df["C.Clutch","low"],2)`,`r round(difference_curvs_df["C.Clutch","high"],2)`] &  \\  
`r round(difference_curvs_df["C.Diam:Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Diam:Pref","low"],2)`,`r round(difference_curvs_df["C.Diam:Pref","high"],2)`] & `r round(difference_curvs_df["C.Clutch:Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Clutch:Pref","low"],2)`,`r round(difference_curvs_df["C.Clutch:Pref","high"],2)`] & \textbf{`r round(difference_curvs_df["C.Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Pref","low"],2)`,`r round(difference_curvs_df["C.Pref","high"],2)`]} \end{pmatrix}$$

@@

```{r Evolvability, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:Evolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for each food-web treatment. We found that the curvature of the removal food web decreased evolvability in 71% of the G-matrices (i.e. the change in evolvability was negative for 71% of the simulations), suggesting that the loss of consumers tended to decrease evolutionary potential of traits in our study."}
knitr::include_graphics("../analyses/delta_evolvability.pdf")
```

@@

\begin{table}[h]
\caption{Standardized selection gradients acting on egg parasitoids (\textit{Platygaster} sp.)}
\label{Table:ExtendedGradients}
\centering
\begin{tabular}{lc}
\\ 
\hline
\textbf{Selection gradient} & \textbf{Contrast = Original - Removal}  \\ 
\hline
$\beta_{\text{Diam}}$ &

@@

```{r EggPtoid_Selection, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on egg parasitoids (*Platygaster* sp.). The bold line represents the average difference in the probability of observing the egg parasitoid (original minus removal of larval parastioids) as a function of gall midge oviposition preference. Thin lines represent bootstrapped replicates to show the uncertainty in selection. For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates. The decrease in the probability of observing egg parasitoids at high gall-midge densities indicate that larval parasitoids impose nonlinear selection on egg parasitoids."}
knitr::include_graphics("../analyses/selection_on_Platygaster.pdf")
```

@@

<!-- Generality of results -->
The generality of our results likely depends on the relative abundance and functional differences between consumers in a community. For example, if consumers do not differ from each other, then we do not expect the loss of consumers to modify evolutionary constraints. Also, many consumers may be at too low of abundances to impose selection on their resources. Rank abundance curves [@Preston1948] and the disproportionate number of weak interactions in diverse communities [@Paine1992] support this notion. This logic suggests that we may not have observed the effects we did if we had only removed one larval parasitoid, because each species had relatively low abundance [@Barbour2016] and they likely share similar ecological roles. When consumers are functionally different and abundant though, the effect of consumer loss will depend on whether different species impose conflicting selection pressures or select for distinct traits. For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997]. Recent studies in this system have shown that decreases in the relative abundance of birds, due to either small patch sizes [@Start2016] or proximity to urban areas [@Start2018] causes a shift from neutral to directional selection on gall size. On the other hand, different consumers may impose selection on different traits, favoring a particular combination of traits and thus greater selective constraints. Examples of this include strong genetic covariances in plant resistance to different insect herbivores [@Maddox1990; @Wise2007; @Wise2013], although there are also examples where these covariances are weak [@Roche1997; @Barbour2015], or vary from year-to-year [@Johnson2007]. We suggest that gaining predictive insight to the evolutionary consequences of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions [@Bascompte2009]. <!--We suggest that gaining predictive insight to the effects of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions.-->

@@

<!--Indirect evolutionary effects-->
Our results suggest that the loss of consumers may not only directly affect connected species, but also result in indirect evolutionary effects. In our study, this indirect effect arises from egg parasitoids being released from intraguild predation when we excluded larval parasitoids. This release occurs more on trees with high larval densities, which could intensify selection on gall midge oviposition preference. A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Pilson1996; @Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @Start2019]. If indirect evolutionary effects are common [@Miller1996; @Walsh2013; @Guimaraes2017], then predicting evolutionary trajectories resulting from the loss of consumers will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.

@@

\begin{table}[h]
\caption{Standardized selection gradients imposed by larval parasitoids on gall midges in the original food web. This gives insight to selection acting on gall midges in the absence of the dominant egg parasitoid.}
\label{Table:LarvalGradients}
\centering
\begin{tabular}{lc}
\\ 
\hline
\textbf{Selection gradient} & \textbf{Larval Parasitoids} \\ % & \textbf{Original} 
\hline
$\beta_{\text{Diam}}$ & 
%\textbf{
%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,2)` [
%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } & 
\textbf{
`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam")$mean,2)` [
`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } \\

@@

```{r LarvalPtoid Evolvability, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:LarvalPtoidEvolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for selection in the absence of egg parasitoids vs. the original food web. We found that the curvature imposed by the loss of egg parasitoids decreased evolvability in 57% of the G-matrices (i.e. the change in evolvability was negative for 57% of the simulations), which is smaller in magnitude, but in the same direction, as the effects of losing larval parasitoids."}
knitr::include_graphics("../analyses/larvalptoid_delta_evolvability.pdf")
```
